# Pietalib my private R functions 

| [home](http://www.compbio.dundee.ac.uk/user/pschofield/index.html) | 
[projects](http://www.compbio.dundee.ac.uk/user/pschofield/private/index.html) | 
[pietalib](http://www.compbio.dundee.ac.uk/user/pschofield/Projects/pietalib/index.html) | 

```{r setupPage,echo=FALSE,include=FALSE}
require(pietalib)
localDir <- "/Users/pschofield/"
fileName <- "index"
projName <- "pietalib"
projDir <- paste0("/homes/pschofield/Projects/",projName,"/")
urlStub <- paste0("/PietaSchofield/",projName,"/")
if(FALSE){
  knit(input=paste0(localDir,"git_hub/",projName,"/wiki/",fileName,".Rmd"),
       output=paste0(localDir,"git_hub/",projName,".wiki/Home.md"))

  buildAll(projName,fileName,outdir=paste0(projDir,"web"),
           indir=paste0(localDir,"git_hub/",projName,"/wiki/"),explicit=T)
}
```

###Introduction

This page attempts to document the creation of my pietalib personal package of function.
I am attempting to do this outside RStudio using the [devtools](http://cran.r-project.org/web/packages/devtools/index.html) package from the command line, and [Hadley Wickham's Book](http://r-pkgs.had.co.nz) as a reference

```{r pietalibDev, eval=FALSE}
# change to the development directory
setwd("/Users/pschofield/git_hub/pietalib")
# create a test directory
devtools::use_testthat()
# create the documentation from the roxygen comments in the R sources
devtools::document()
# load the package for testing
devtools::load_all()
# run the test scripts stored in the tests subdirectory
devtools::test()
# install the packages so it can be used outwith the source directory
devtools::install(reload=T)
# get the help for one of the functions
help(subScript)
devtools::use_data_raw()
devtools::use_vignette("pietalib")
```

###January 20, 2015

Moved the code base to a [GitHub](https://github.com/PietaSchofield/pietalib) repository like the SpikeNorm one

###January 23, 2015

Some ammendments
- Started adding timelogging stuff for quick loading of OfficeTime data
- Added cores to subScript
- Added a function rsh to run remote command
- Added a function to save a list of package citations to a bib file for
  importing into endnote

###February 19, 2015

Fix the prism parser

```{r feb19, results="asis"}
filename <- "/Users/pschofield/Projects/sumo_rth/data/qPCRresults/Figure_S10JK/CHD4.pzfx"
dat <- readPrism(filename)
kable(dat)
```

###March 25, 2015

Edited the [timesheet](/user/pschofield/Projects/timesheets/) management functions to have a from and to date.

Added a function to pull some grid engine info from the cluster.
